---
title: "Priming of reversals and stability in perceptually coupled multistable displays"
author: "Alexander (Sasha) Pastukhov"
date: "20 March 2018"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 3
  github_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = TRUE
)

library("boot")
library("extrafont")
library('knitr')
library('tidyverse')
library('lme4')
library('lmerTest')
library('BayesFactor')
library('MuMIn')
library("predictmeans")
library('binom')
library('car')

loadfonts()
```

This document contains the entire analysis code to generate descriptive statistics and figures for the manuscript.

# Preprocessing

First, we merge files of individual observers into a single table

```{r Merging data, message=FALSE}
rm(list= ls())

reports <- tibble(filename= list.files(path='Data', pattern= 'csv$')) %>%
  rowwise() %>%
  do(read_csv2(file.path('Data', .$filename))) %>%
  
  # converting Python True/False to R boolean
  mutate(Yellow= Yellow == 'True') %>%
  
  # making observer a factor
  ungroup() %>%
  mutate(Observer = as.factor(Observer))

```

Next, we create additional variables that merge `left`/`right` triggers and reports into a `single` trigger and report.

```{r Merge single triggers/responses}

reports <- reports %>%
  # exogenous trigger
  mutate(Trigger = fct_recode(Switch, unperturbed= 'neither', 
                                      'single trigger'= 'left', 
                                      'single trigger'= 'right', 
                                      'double trigger'= 'both'), 
         Trigger = fct_relevel(Trigger, 'unperturbed', 'single trigger', 'double trigger')) %>%
  # responses
  mutate(ResponseMerged = fct_recode(Response, 'both stable'= 'neither', 
                              'single switch'= 'left', 
                              'single switch'= 'right', 
                              'both switched'= 'both'), 
         ResponseMerged = fct_relevel(ResponseMerged, 'both stable', 'single switch', 'both switched'))
```

We also recode `Gap`from numeric values into a factor into a new `Layout` variable for plotting.
```{r Recode Gap}
reports <- reports %>%
  mutate(Layout = fct_recode(as.character(Gap), overlap = '-0.15', touching= '0', gap= '0.15'), 
         Layout = fct_relevel(Layout, 'overlap', 'touching', 'gap'))
```

# Probability of the report given the exogenous trigger type, the spatial layout, and timing of the switch
This generates _Figure X_ and the associated _Table X_. 


```{r Function to bootstrap CI for group means}
#' Computes variable mean and 95% bootstrapped bca CI 
#'
#' @param data data table
#' @param variableOfInterest name of the column to analyze
#' @param seed seed for the random numbers generator (to make CIs reproducable). NULL means no seeding
#' @param avgFun function used for computing average value, defaults to 'mean'
#' @param R number of bootstrap iterations, defaults to 2000
#'
#' @return table with columns bcaLower, meanValue, bcaUpper
getvariableCI <- function(data, R= 2000){
  sampled_mean <- function(data, index){
    return(mean(data[index]))
  }
  
  # sample mean
  sampledMean <- boot(data= data$report_proportion,
                      statistic = sampled_mean,
                      R= R)
  
  # compute CIs
  sampledCI <- boot.ci(sampledMean, type= 'bca')

  # package for output
  data.frame(bcaLower= sampledCI$bca[4], meanValue= mean(data$report_proportion), bcaUpper= sampledCI$bca[5])
}
```


```{r plotting theme}
plot_theme <- 
  theme(text=element_text(family="Arial"), 
        axis.text.x = element_text(size = 8, colour = 'black'), 
        axis.text.y = element_text(size = 8, colour = 'black'), 
        axis.title.x = element_text(size = 10), 
        axis.title.y = element_text(size = 10), 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x = element_blank(), 
        panel.grid.major.y =  element_line(size = 0.24), 
        panel.grid.minor.y =  element_line(size = 0.24), 
        axis.ticks = element_line(size = 0.24))
                    
```

First, we plot group averages grouped by the _response type_. However, the proportion is computed relative to the _trigger type_ and, therefore, values with each plot do not add up to 1. Rather, values for the same _trigger type_ across all plots add up to 1.

```{r Report probability plot}
observer_average_report <- reports %>%
    # counting each type of report for all available combinations of exogenous trigger and layouts  
    dplyr::group_by(Observer, Layout, Trigger, ResponseMerged) %>%
    dplyr::summarize(response_count= n()) %>%
    dplyr::ungroup() %>%
  
    # filling out missing combinations with zero report counts
    tidyr::complete(Observer, Layout, Trigger, ResponseMerged, fill= list(response_count = 0)) %>%

    # computing proportion of given report types for all combinations of exogenous trigger and layouts
    # first, at the level of individual observers
    dplyr::group_by(Observer, Layout, Trigger) %>%
    dplyr::mutate(report_proportion= response_count/sum(response_count)) %>%
    dplyr::ungroup()


set.seed(711467)

group_average_report <- observer_average_report %>%
    # then, at the group level
    dplyr::group_by(Layout, Trigger, ResponseMerged) %>%
    dplyr::do(getvariableCI(.))

ggplot(data= group_average_report,
       aes(x= Layout, y= meanValue, ymin= bcaLower,  ymax= bcaUpper,
           color= ResponseMerged, fill= ResponseMerged, linetype= ResponseMerged,
           shape= ResponseMerged, group= ResponseMerged))+
  geom_line() +
  geom_point(size=3) +
  geom_errorbar(width=0.1, linetype= 'solid') +
  xlab('Layout') +
  ylab('P(report | layout, exogenous trigger)')+
  theme(legend.position='none') +
  facet_grid(. ~ Trigger)+
  scale_shape_manual(values=c(21, 22, 23)) + 
  plot_theme

ggsave('Trigger type and layout.pdf', width= 14, height= 8, units = 'cm', useDingbats= FALSE)
```

Next we analyze how the spatial layout and the type of the exogenous trigger (single or double) alters the probability of **each** report. Please note that we are **excluding** unperturbed trials from the analysis as our focus is on single/double trigger difference.

```{r LMM of response based on trigger and layout}
effect_on_reports <- function(observer_reports, response_type, matching_trigger){
  observer_averages <- observer_reports %>%
      # counting each type of report for all available combinations of exogenous trigger and layouts  
      dplyr::group_by(Observer, Layout, Gap, Trigger, ResponseMerged, SwitchTime) %>%
      dplyr::summarize(response_count= n()) %>%
      dplyr::ungroup() %>%
    
      # filling out missing combinations with zero report counts
      tidyr::complete(Observer, Layout, Gap, Trigger, ResponseMerged, SwitchTime, fill= list(response_count = 0)) %>%
  
      # computing proportion of given report types for all combinations of exogenous trigger and layouts
      # first, at the level of individual observers
      dplyr::group_by(Observer, Layout, Gap, Trigger, SwitchTime) %>%
      dplyr::mutate(report_proportion= response_count/sum(response_count), 
                    report_proportion= ifelse(is.na(report_proportion), 0, report_proportion), 
                    report_logit= car::logit(report_proportion, adjust= 0.025)) %>%
      dplyr::ungroup()  
  
  selected_reports <- observer_averages %>%
      dplyr::filter((ResponseMerged==response_type) & (Trigger!='unperturbed')) %>%
      mutate(Trigger= fct_drop(Trigger))

  if (!is.null(matching_trigger)){
    selected_reports <- selected_reports %>%
      mutate(Trigger= fct_relevel(Trigger, matching_trigger))
  }
  
  # performing multi-level linear mixed modelling
  `null model` <- lme4::lmer(report_logit ~ 1 + (1|Observer), data= selected_reports, REML= FALSE)
  `+ trigger time` <- update(`null model`, .~. + SwitchTime)
  `+ layout` <- update(`+ trigger time`, .~. + Gap)
  `+ trigger type` <- update(`+ layout`, .~. + Trigger)
  `+ type x layout` <- update(`+ trigger type`, .~. + Trigger*Gap)
  anova_table <- anova(`null model`, `+ trigger time`, `+ layout`, `+ trigger type`, `+ type x layout`)
  models <- list(`null model`, `+ trigger time`, `+ layout`, `+ trigger type`, `+ type x layout`)
  
  # Permutation ANOVA + Effect size
  anova_table$`p-perm` <- NA
  anova_table$R2m <- NA
  anova_table$R2c <- NA
  for(imodel1 in seq(2, length(models))){
    # current_pair <- permlmer(models[[imodel1-1]], models[[imodel1]], perms = 9999)
    # anova_table$`p-perm`[imodel1] <- current_pair$`Perm-p`[2]


    effect_size <- data.frame(r.squaredGLMM(models[[imodel1]]))
    anova_table$R2m[imodel1] <- effect_size$R2m
    anova_table$R2c[imodel1] <- effect_size$R2c
  }
    
  # Bayesian ANOVA
  bf_df <-
    selected_reports %>%
    ungroup() %>%
    mutate(Observer = as.factor(as.numeric(as.factor(Observer))), # otherwise something breaks
           SwitchTime = as.factor(SwitchTime),
           Gap = as.factor(Gap),
           Trigger = as.factor(Trigger))
  
  bf_random <- lmBF(report_logit ~ Observer, data=bf_df, whichRandom = "Observer")
  bf_time <- lmBF(report_logit ~ SwitchTime + Observer, data=bf_df, whichRandom = "Observer")
  bf_layout <- lmBF(report_logit ~ SwitchTime + Layout + Observer, data=bf_df, whichRandom = "Observer")
  bf_trigger <- lmBF(report_logit ~ SwitchTime + Layout + Trigger + Observer, data=bf_df, whichRandom = "Observer")
  bf_trigger_layout <- lmBF(report_logit ~ SwitchTime + Layout + Trigger + Layout:Trigger + Observer, data=bf_df, whichRandom = "Observer")
  bf_models <- list(bf_random, bf_time, bf_layout, bf_trigger, bf_trigger_layout)

  BFs <- rep(NA, length(bf_models))
  for(iM in 2:length(bf_models)){
    BFs[iM] <- extractBF(bf_models[[iM]])$bf[1] /  extractBF(bf_models[[iM-1]])$bf[1]
  }
  anova_table$bf <- BFs
  list(anova_table, `+ layout`)
}
```

We use linear mixed models for each type of the response.

Effect on **both stable** response

```{r Response LMM and BF analysis}
set.seed(218929)
both_stable_results <- effect_on_reports(reports, 'both stable', NULL)
both_stable_results[[1]] %>% 
  kable(., digits =  c(0, 0, 0, 0, 0, 1, 0, 4, 4, 2, 2, 1))

summary(both_stable_results[[2]])
```

```{r Single switch}
set.seed(306731)
single_switch_results <- effect_on_reports(reports, 'single switch', 'single trigger')
single_switch_results[[1]] %>% 
  kable(., digits =  c(0, 0, 0, 0, 0, 1, 0, 4, 4, 2, 2, 1))

summary(single_switch_results[[2]])
```


```{r both  switched}
set.seed(321312)
both_switched_results <- effect_on_reports(reports, 'both switched', 'double trigger')
both_switched_results[[1]] %>% 
  kable(., digits =  c(0, 0, 0, 0, 0, 1, 0, 4, 4, 2, 2, 1))

summary(both_switched_results[[2]])
```

```{r}
c(both_stable_results[[1]]$`Pr(>Chisq)`, 
  single_switch_results[[1]]$`Pr(>Chisq)`,
  both_switched_results[[1]]$`Pr(>Chisq)`) %>%
  # na.omit() %>%
  p.adjust(.) %>%
  kable(digits = c(4))
```





# Effect of the previous response, a.k.a. Priming

```{r Number of prior switches}

# adding information about the prior Response
reports_with_history <- reports %>%
  mutate(PreviousResponse_merged = lag(ResponseMerged), 
         PreviousResponse = lag(Response), 
         PreviousLayout = lag(Layout)) %>%
  
  # we will ignore first trial in each block, as they lack history
  filter(!is.na(PreviousResponse))
  
observer_report_given_history <- reports_with_history %>%
  dplyr::group_by(Observer, Layout,  PreviousResponse_merged, ResponseMerged) %>%
  dplyr::summarize(response_count= n()) %>%
  dplyr::ungroup() %>%  

  # filling out missing combinations with zero report counts
  tidyr::complete(Observer, Layout, PreviousResponse_merged, ResponseMerged, fill= list(response_count = 0)) %>% 
  
  # computing proportion of given report types for all combinations of prior Response and layouts
  dplyr::group_by(Observer, Layout, PreviousResponse_merged) %>%
  dplyr::mutate(report_proportion= response_count/sum(response_count)) %>%
  dplyr::ungroup()


group_report_given_history <- observer_report_given_history %>%
    dplyr::group_by(Observer, Layout, PreviousResponse_merged) %>%
    dplyr::mutate(report_proportion= response_count/sum(response_count)) %>%
    # then, at the group level
    dplyr::group_by(Layout, PreviousResponse_merged, ResponseMerged) %>%
    dplyr::do(getvariableCI(.)) %>%
    dplyr::rename('Previous Response' = PreviousResponse_merged)

# group_report_given_history <- observer_report_given_history %>%
#     dplyr::group_by(Observer, Layout, PreviousResponse_merged) %>%
#     dplyr::mutate(report_proportion= response_count/sum(response_count)) %>%
#     # then, at the group level
#     dplyr::group_by(Layout, PreviousResponse_merged, ResponseMerged) %>%
#     dplyr::summarize(Preport= mean(report_proportion),
#                      SERRreport= sd(report_proportion)/sqrt(n()-1)) %>%
#     dplyr::rename('Previous Response' = PreviousResponse_merged)


ggplot(data= group_report_given_history,
       aes(x= Layout, y= meanValue, ymin= bcaLower, ymax= bcaUpper,
           color= `Previous Response`, fill= `Previous Response`, linetype= `Previous Response`,
           shape= `Previous Response`, group= `Previous Response`))+
  geom_line() +
  geom_point(size=3) +
  geom_errorbar(width=0.1, linetype= 'solid') +
  xlab('Layout') +
  ylab('P(report | layout, prior Response)')+
  theme(legend.position='none') +
  facet_grid(. ~ ResponseMerged)+
  scale_shape_manual(values=c(21, 22, 23)) +
  plot_theme



# ggplot(data= group_report_given_history,
#        aes(x= Layout, y= meanValue, ymin= bcaLower, ymax= bcaUpper,
#            color= ResponseMerged, fill= ResponseMerged, linetype= ResponseMerged,
#            shape= ResponseMerged, group= ResponseMerged))+
#   geom_line() +
#   geom_point(size=3) +
#   geom_errorbar(width=0.1, linetype= 'solid') +
#   xlab('Layout') +
#   ylab('P(report | layout, prior Response)')+
#   theme(legend.position='none') +
#   facet_grid(. ~ `Previous Response`)+
#   scale_shape_manual(values=c(21, 22, 23)) + 
#   plot_theme

ggsave('Priming.pdf', width= 14, height= 8, units = 'cm', useDingbats= FALSE)
# ggsave('Priming.pdf', width= 20, height= 12, units = 'cm', useDingbats= FALSE)
```


```{r LMM of response based on priming and layout}
priming_on_reports <- function(observer_reports, response_type){
  observer_averages <-
      observer_reports %>%
      # counting each type of report for all available combinations of exogenous trigger and layouts  
      dplyr::group_by(Observer, Gap, PreviousResponse_merged, ResponseMerged) %>%
      dplyr::summarize(response_count= n()) %>%
      dplyr::ungroup() %>%
    
      # filling out missing combinations with zero report counts
      tidyr::complete(Observer, Gap, PreviousResponse_merged, ResponseMerged, fill= list(response_count = 0)) %>%
  
      # computing proportion of given report types for all combinations of exogenous trigger and layouts
      # first, at the level of individual observers
      dplyr::group_by(Observer, Gap, PreviousResponse_merged) %>%
      dplyr::mutate(report_proportion= response_count/sum(response_count), 
                    report_proportion= ifelse(is.na(report_proportion), 0, report_proportion), 
                    report_logit= car::logit(report_proportion, adjust= 0.025)) %>%
      dplyr::ungroup()  
  
  selected_reports <- observer_averages %>%
      dplyr::filter((ResponseMerged==response_type)) %>%
      mutate(PreviousResponse_merged= fct_relevel(PreviousResponse_merged, response_type))
    

  # using lmerTest to compare other responses to the target one
  sorted_reports <- selected_reports %>%
    mutate(PreviousResponse_merged= fct_relevel(PreviousResponse_merged, response_type))
  
  `random effects` <- lme4::lmer(report_logit ~ (1|Observer), data= sorted_reports)
  `+ layout` <- update(`random effects`, .~. + Gap)
  `+ prior response` <- update(`+ layout`, .~. + PreviousResponse_merged)
  anova_table <- anova(`random effects`, `+ layout`, `+ prior response`)
  
  models <- list(`random effects`, `+ layout`, `+ prior response`)
  
  # Permutation ANOVA + Effect size
  anova_table$R2m <- NA
  anova_table$R2c <- NA
  for(imodel1 in seq(2, length(models))){
    effect_size <- data.frame(r.squaredGLMM(models[[imodel1]]))
    anova_table$R2m[imodel1] <- effect_size$R2m
    anova_table$R2c[imodel1] <- effect_size$R2c
  }
    
  # Bayesian ANOVA
  bf_df <-
    sorted_reports %>%
    ungroup() %>%
    mutate(Observer = as.factor(as.numeric(as.factor(Observer))), # otherwise something breaks
           Layout = as.factor(Gap),
           PreviousResponse_merged = as.factor(PreviousResponse_merged))
  
  bf_random <- lmBF(report_logit ~ Observer, data=bf_df, whichRandom = "Observer")
  bf_layout <- lmBF(report_logit ~ Layout + Observer, data=bf_df, whichRandom = "Observer")
  bf_prior_response <- lmBF(report_logit ~ PreviousResponse_merged + Layout + Observer, data=bf_df, whichRandom = "Observer")
  bf_models <- list(bf_random, bf_layout, bf_prior_response)

  BFs <- rep(NA, length(bf_models))
  for(iM in 2:length(bf_models)){
    BFs[iM] <- extractBF(bf_models[[iM]])$bf[1] /  extractBF(bf_models[[iM-1]])$bf[1]
  }
  anova_table$bf <- BFs
  
  
  lmTestModel <- lmerTest::lmer(report_logit ~ Gap + PreviousResponse_merged + (1|Observer), data= sorted_reports)
  

    list('anova'= anova_table,
       'lmertest'= lmTestModel)
}

# modelling each response type

```

```{r}
set.seed(538798)
both_stable_results <- priming_on_reports(reports_with_history, 'both stable')
both_stable_results[['anova']] %>%
  data.frame() %>%
  kable(digits =  c(0, 0, 0, 0, 0, 1, 0, 4, 2, 2, 1))
summary(both_stable_results[[2]])
```


```{r}
set.seed(95100)
single_switch_results <- priming_on_reports(reports_with_history, 'single switch')
single_switch_results[["anova"]] %>%
  data.frame() 
%>%
  kable(digits =  c(0, 0, 0, 0, 0, 1, 0, 4, 2, 2, 1))

summary(single_switch_results[[2]])
```

```{r}
set.seed(736405)
both_switched_results <- priming_on_reports(reports_with_history, 'both switched')
both_switched_results[["anova"]] %>%
  data.frame() %>%
  kable(digits =  c(0, 0, 0, 0, 0, 1, 0, 4, 2, 2, 1))
summary(both_switched_results[[2]])
```

```{r Adjusting p-values for ANOVA}
# adjusting p-values for multiple comparisons 
c(both_stable_results[["anova"]]$`Pr(>Chisq)`, 
  single_switch_results[["anova"]]$`Pr(>Chisq)`,
  both_switched_results[["anova"]]$`Pr(>Chisq)`) %>%
  na.omit() %>%
  p.adjust(.) %>%
  kable(digits = c(4))
```

# Location-specificity of priming for single switch only

Here, we are looking only at the `single switch` responses that were preceded also by `single switch` responses. Specifically, we are interested the layout would influence whether the second reponse is more likely to appear on the same side as the previous one. 


```{r Side-specificity for single switch priming}
single_reports <- reports_with_history %>%
  filter(ResponseMerged == 'single switch' & PreviousResponse %in% c('left', 'right')) %>%
  mutate(ResponseSide= ifelse(Response== PreviousResponse, 'same', 'opposite')) %>%
  group_by(Observer, Layout) %>%
  summarize(Psame_side= mean(ResponseSide == 'same')) %>%
  ungroup() %>%
  tidyr::complete(Observer, Layout, fill= list(Psame_side = 0))

# plotting 
single_reports %>%
  mutate(Layout= fct_relevel(Layout, 'overlap', 'touching', 'gap')) %>%
ggplot(aes(x= Layout, y= Psame_side, group= Layout, color= Observer))+
  geom_boxplot(outlier.shape = NA)+
  geom_point(position = position_jitter(width = 0.2))+
  theme(legend.position = 'none') + 
  ylab('P(same side)')

# ggsave('Priming-Side.pdf', width= 16, height= 16, units = 'cm', useDingbats= FALSE)

# statistical comparison of gap condition versus two other layouts
single_reports <- single_reports %>%
  ungroup() %>%
  mutate(Layout= fct_relevel(Layout, 'gap'), 
         Plogit= car::logit(Psame_side, adjust = 0.025))

summary(lmerTest::lmer(Plogit ~ Layout + (1|Observer), data= single_reports))$coefficients %>%
  kable(., col.names = c('Estimate', 'Std. Error', 'df', '$t$', '$p$'), 
        digits = c(4, 2, 1, 1, 4))


t.test(single_reports$Plogit[single_reports$Layout == 'overlap'], mu = 0.5)
t.test(single_reports$Plogit[single_reports$Layout == 'touching'], mu = 0.5)
t.test(single_reports$Plogit[single_reports$Layout == 'gap'], mu = 0.5)

```


```{r}
right_sphere_switched <-
  reports_with_history %>%
  group_by(Observer, PreviousResponse, Layout) %>%
  summarize(PmatchingSingleSwitch= sum(Response=='right')/n()) %>%
  ungroup() %>%
  data.frame() %>%
# filling out missing combinations with zero report counts
  tidyr::complete(Observer, PreviousResponse, Layout, fill= list(PmatchingSingleSwitch = 0)) %>%
  # focusing on single switches
  filter(PreviousResponse %in% c('left', 'right')) %>%
  mutate(ResponseOnSameSide= PreviousResponse == 'right')


left_sphere_switched <-
  reports_with_history %>%
  group_by(Observer, PreviousResponse, Layout) %>%
  summarize(PmatchingSingleSwitch= sum(Response=='left')/n()) %>%
  ungroup() %>%
  # filling out missing combinations with zero report counts
  tidyr::complete(Observer, PreviousResponse, Layout,
                  fill= list(PmatchingSingleSwitch = 0)) %>% # focusing on single switches
  filter(PreviousResponse %in% c('left', 'right')) %>%
  mutate(ResponseOnSameSide= PreviousResponse == 'left')

side_history <-
  left_sphere_switched %>%
  rbind(right_sphere_switched) %>%
  group_by(Observer, Layout, ResponseOnSameSide) %>%
  summarize(Pmatch= mean(PmatchingSingleSwitch, na.rm = TRUE), 
            Plog = car::logit(Pmatch, adjust = 0.0025)) %>%
  ungroup() %>%
  mutate(Observer = as.factor(as.numeric(as.factor(Observer))), 
         ResponseOnSameSide = as.factor(ResponseOnSameSide))

group_side_history <- 
  side_history %>%
  group_by(Layout,  ResponseOnSameSide) %>%
  summarise(Pmean= mean(Pmatch, na.rm= TRUE),
            Pserr= sd(Pmatch, na.rm= TRUE)/sqrt(n()-1))
  
ggplot(data= group_side_history,
  aes(x= Layout, y= Pmean, ymin= Pmean-Pserr, ymax= Pmean+Pserr,
  color= ResponseOnSameSide, fill= ResponseOnSameSide, group= ResponseOnSameSide)) +
  geom_errorbar()+
  geom_line()+
  geom_point() + 
  scale_color_brewer(palette="Dark2") + 
  plot_theme + 
  theme(legend.position = "none")
  

ggsave("side-specificity.pdf", width = 6, height = 7, units = "cm", useDingbats = FALSE)
```


Side-specific priming: overlap
```{r side overlap}
overlap_lmm <-
  side_history %>%
  filter(Layout == "overlap") %>%
  lmerTest::lmer(Plog ~ ResponseOnSameSide + (1|Observer), data=.) %>%
  summary()

kable(data.frame(overlap_lmm$coefficients), 
      digits = c(1, 1, 0, 1, 4))

set.seed(6589)
side_history %>%
  filter(Layout == "overlap") %>%
  anovaBF(Plog ~ ResponseOnSameSide + Observer, data=., whichRandom = "Observer")
```

Side-specific priming: touch
```{r side touch}
touch_lmm <-
  side_history %>%
  filter(Layout == "touching") %>%
  lmerTest::lmer(Plog ~ ResponseOnSameSide + (1|Observer), data=.) %>%
  summary()

kable(data.frame(touch_lmm$coefficients), 
      digits = c(1, 1, 0, 1, 4))

set.seed(545633)
side_history %>%
  filter(Layout == "touching") %>%
  anovaBF(Plog ~ ResponseOnSameSide + Observer, data=., whichRandom = "Observer")
```

Side-specific priming: gap
```{r side gap}
gap_lmm <-
  side_history %>%
  filter(Layout == "gap") %>%
  lmerTest::lmer(Plog ~ ResponseOnSameSide + (1|Observer), data=.) %>%
  summary()

kable(data.frame(gap_lmm$coefficients), 
      digits = c(1, 1, 0, 1, 4))

set.seed(208426)
side_history %>%
  filter(Layout == "gap") %>%
  anovaBF(Plog ~ ResponseOnSameSide + Observer, data=., whichRandom = "Observer")
```

```{r}
p.adjust(c(data.frame(overlap_lmm$coefficients)$Pr...t..[2],
           data.frame(touch_lmm$coefficients)$Pr...t..[2], 
           data.frame(gap_lmm$coefficients)$Pr...t..[2]), method="holm") %>%
  kable(digits= c(4))
```
